NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-06-08 paper/itemizedReviewResponse.tex

Summary Review

The Summary Review
Reviewers were split on whether or not to accept the paper. R2 and R4 rated the paper very highly (5 and 4.5), while R1 and R3 gave lower scores of neutral or weak reject (3 and 2.5). As the scores average to 3.75, and because the primary and secondary reviewers are in agreement, we are advocating for an "Accept". However, the authors should pay careful attention to the comments by reviewers, and use the time remaining before the next version is due to revise the paper for clarity, to emphasize the main contributions of the paper, to provide rationale for the design choices, to provide more detailed information about the domain-expert collaborators, and to better justify the results of the task analysis. Some reviewers advocated for reducing the number of usage scenarios and providing a more in-depth examination of a single scenario, or a scenario composed of a series of sub-investigations. On the other hand, other reviewers found the breadth of potential analyses to be a positive component of the paper.

R1:
+ interesting topic
+ usage scenarios are interesting
- description of NLP NN and attention models are not sufficiently detailed in the paper
- details of collaboration with domain experts are missing
- justification of tasks are not sufficiently detailed
- differences between graph and matrix view should be explained in more detail
- density contour in the prediction view needs to be explained in more detail
- claims about extension of visualization system to non-NLI tasks is not supported
- need to clarify difference between proposed perturbation-driven analysis and gradient-based analysis
- qualitative evaluation is weak

R2:
+ important area for visualization research
+ article is well-written
+ application with linked views is well-designed and powerful
+ system supports debugging of inference models
- scalability of system is not discussed

R3: 
- article is dense and difficult to read
- rationale for design choices are not clear
- core contributions are not highlighted, too much emphasis on background material (explanation of NLI), not enough on the visualization system itself
- claims based on user evaluation aren?t supported

Reviewer 1
Paper type
Application / Design Study
Expertise
Knowledgeable
Overall Rating
<b>3 - Possible Accept</b><br/> The paper is not acceptable in its current state, but might be made acceptable with significant revisions within the conference review cycle.<br/>If the specified revisions are addressed fully and effectively I may be able to return a score of '4 - Accept'.
Supplemental Materials
Acceptable
Justification
This paper presents an interactive visualization system for analyzing natural language inference models with attention mechanisms. The perturbation-driven paradigm proposed by the authors are well implemented with various visualization components. However, there is still room to improve the presentation of the task analysis and the system design. The contribution of the visualization tool is limited to NLI models and it?s unclear how it could be extended to support the analysis of other tasks/models.
The Review
This paper presents an interactive visualization system, NLIZE, for analyzing natural language inference models. Based on a perturbation-driven exploration scheme and a regularized optimization scheme, the system allows users to interrogate how the prediction or the model would change if the input, attention or the predicted label changed. The system implemented visualization as a list of flexible visualization components that allow easy integration. The usefulness of the system is demonstrated through five usage scenarios and the system is evaluated through the feedback from both VIS and NLP researchers.

Understanding and analyzing the inner mechanisms of deep neural nets for NLP tasks is an interesting and unexplored topic. A flexible visualization tool might indeed help researchers develop more powerful models. The main contribution of this paper is the novel perturbation-driven scheme that allows domain experts flexibly explore the stability and the internals of an NLI model. The proposed analytic scheme treats a trained model as dynamic and allows modifications of the model on the fly.

The proposed idea is interesting, and the flexible design of the tool may also increase the adoption of the tool. The usage scenarios also look interesting, especially the Scenario 3. Does the result to some extent suggest that the attention mechanism is not a very efficient component in this task? I expect the authors dig it further.

However, the current shape of this paper may require a major revision before it is in an acceptable shape.

My major concern is the presentation of the paper.

1. In Section 2, the neural net in NLP and attention mechanisms are introduced. But the descriptions are unsatisfactory. There is no formal definition or description of the model and the attention mechanism. It?s still unclear how the attention mechanism is applied in the model. I would suggest the authors include a concise and formal introduction in the background part and include some formula.

2. In Section 4, the paper indicates that the system is developed under a long-term collaboration with NLP experts, but there is no description describing the details of the collaboration (the number of experts, the length and the form of the collaboration, the frequency of the meetings). It?s not until Section 7 did I learn that there are 2 NLP experts in collaboration. The task analysis can also be improved by including more detailed justification of the three tasks.

3. The presentation of the system design in Section 5 could be improved. 
- In Section 5.2, Attention View include both a bipartite graph and a matrix view, which visualize the same information. From the description of the paper, the graph view is only good for highlighting the most dominant alignments. I suspect that matrix view can also reveal the most dominant alignments by identifying the most salient color. Please justify the design decision. 
- It?s unclear how the simplification of attention representation is done from Section 5.2, please include more details.
- In Section 5.3, how do you compute the density contour? Why is a contour needed in the analysis?
- It?s better if the authors present the relation between Section 5.3 and 5.4 in a clearer way. It?s confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4. I suggest put the algorithm along with the perturbation-driven paradigm at the beginning of Section 5

Except for the presentation issue, the contribution of this paper is somewhat limited to only NLI models with attention mechanisms. It?s not sure how the visualization can be easily extended for other NLP tasks. For example, I am not sure how the proposed visualization can easily adapt to machine translation, considering that there are no neutral/contradiction/entailment labels.

In addition, the perturbation-driven scheme is somewhat related to the gradient-based analysis (both are the local analysis of the model on a specific prediction). It is better if the authors discuss the two and differentiate them.

The evaluation is acceptable but a bit weak. There is no description of what questions have the authors asked during the evaluation sessions. It would be better to have formal interviews and ask the participants to perform specific tasks and observe how they performed.

Please also proofread the work and fix typos. For example, the word ?work? in Section 3 should be uncountable; In Section 5.3 ?the three points defines a triangle? -> ?the three points defining a triangle?
Reviewer 2
Paper type
Technique
Expertise
Expert
Overall Rating
<b>5 - Strong Accept</b><br/> The paper is an excellent contribution and should certainly be accepted, possibly with some minor revisions.<br/>It more than meets the quality standard.
Supplemental Materials
Acceptable
Justification
Overall, this is an excellent contribution, it successfully demonstrates the value of visualization, and sheds light on hidden mechanisms performed by complex models.
It also closes the analysis loop by enabling experts to introduce model adjustments and examine their effectiveness in mitigating mis-predictions.
The Review
The authors propose a system to debug the predictions of deep inference models in language domain.
These models focus on predicting whether a hypothesis entails, contradicts, or is neutral to a given premise. 
This is a very essential task in natural language understanding that goes beyond machine translation where the models transform an input language to an output language without being able to evaluate logical entailment between sentences nor to answer questions based on given text.

The system is very well designed and the article is very well written.
The authors employ five linked views to show different facets about the model at varying granularity and at stages in the model pipeline. The visualization design in each of these views is mapped smoothly from the data it shows and the analysis task it serves.
Likewise, the linkage between these views and the corresponding interactions are well suited for debugging purposes. In particular:
- they enable tracing the root cause of certain entailment predictions e.g. by exposing the model attention computed at any selected part of an input sentence.
- they enable examining different perturbations of the input sentence and easily identifying the ones that lead to changes in the prediction, hence revealing the language features behind these predictions and the corresponding attention values computed by the model.
- they enable reducing visual clutter by interactively collapsing irrelevant parts, which improves resolution.
Furthermore, the authors provide auxiliary helps such as grammar dependency tree and a diff heatmap.

In addition, the authors propose a simple method to adjust the model in order to avoid certain prediction errors, and to accordingly examine the effect of such optimizations.

The authors demonstrate five application scenarios on Bowman's NLI large corpus (cited as [24]) for Natural Language Inference.
These scenarios show the power of the proposed system. In particular the system exposes the "decision-making" process of the model, its stability, and the grammar it learns to capture via its attention mechanism, and accordingly enables exploring avenues to correct mispredictions by identifying at which stage they develop.

Finally, the authors discuss the limitations of their system, highlighting inherent difficulty of perturbating textual data without distorting the legibility or the language-wise plausibility of the input (unlike image data were perturbations are easy to impose). They provide sufficient details about their model and a video demonstration of the system in the supplementary.

Few remarks:
- A brief guidance of how to interpret visual patterns that emerge in each view would be very beneficial. In particular, did the authors notice any systematic / repetitive patterns in the triangular prediction view? Do these patterns indicate certain issues in the model / attention / perturbation schemes?
Same thing applies to the attention heatmap, the parameter histograms, and the overview scatterplots in Figure 8 (e.g. does the curve in Figure 8d tell us something?)
- Discuss scalability of the system. Can it visually handle long sentences? Would collapsing the heatmaps help here?
Can it handle a large number of sentences? This is important for the noted future applicability to question answering where the data items can be as large as text documents.
- Explain more about the Bowman's dataset in use [24], its dimensionality, coverage, complexity, language features, etc.
- A brief discussion of the applicability to other languages would be interesting maybe? Any anticipated challenges?
- Add label to the color scale in Figure 3 (the caption mentions attention by just to avoid confusion). Same for Figure 7a (frequency to the vertical axis), Figure 8b, and Figure 9a-c.
- Add narration to the video and maybe include a 1-min self-contained demo of the system before illustrating the use cases in the video.

Language mispredictions (misspelling):
As discussion in [8, 13]
tasks T1-3 (maybe T1-T3?)
correspondance 
studys
Reviewer 3
Paper type
Application / Design Study
Expertise
Knowledgeable
Overall Rating
<b>2.5 - Between Reject and Possible Accept</b><br/>
Supplemental Materials
Acceptable with minor revisions (specify revisions in The Review section)
Justification
This paper presents an application of multiple coordinated views to expert refinement of natural language inferences. The organization and presentation of the paper focuses very heavily on the neural network and natural language aspects of the application. The style of the paper is very dense, and occasionally oddly enthusiastic in tone, making for a very difficult read. The different views in the combined tool are described, but there is little rationale for and analysis of the visual representation choices that went into them.

The application itself seems interesting and appears to have some value, albeit apparently only for a very narrow group of expert users who have a particular mix of technical skills. The several described use cases look useful but as described are largely isolated in their utility; it's unclear how they can be integrated to support the broader analysis efforts of the target users.
The Review
This was a difficult paper to digest. Research on ways to bring together visualization and AI has become popular in the last few years, so the authors are targeting a fast-moving and dense space of possibilities. One of the main challenges in reading this paper was digesting not two but three different pillars of cutting edge work: richly interactive visual analytic tool design, neural networks, and natural language inference modeling. After the teaser image, the paper spends the first four pages on neural networks, NLP, and inference. One has to look hard to detect the lede in the next to last paragraph of the introduction ("Moreover, we propose...") Highlight it!

Even as a visualization-centric researcher who is aware of NNs and has done a little direct work in NLP, I found it hard to connect to the organization and balance of coverage of these topics in the paper. Despite the prominent teaser visualization and the description of individual views in section 5, the paper comes off as very visualization-light. For each view there it's clear what the visual representation is, but the majority of description is dedicated to the underlying mechanics of calculating and thinking about the NL inference. The specific interactions involved are also mostly implied, although I was able to deduce them. They should be made explicit.

More importantly, there is little rationale for the visual representation designs of the various views. The design choices do make sense (at least to an experienced visualization designer) but there are alternatives in each case. It's not clear that the visualization are particularly good or bad for their intended uses as described in section 6. A few questions that arise:

* How does one handle very different sentence lengths in the sentence view?
* What if the sentence structures between premise and hypothesis are not drastically different; will the matrix be as effective, and thus the graph need to be focused on?
* In the matrix view, how hard is it to control rows when they're renormalizing?
* How much reduction in the grammar dependency tree is necessary to combat visual clutter, and how does that relate to the expert's ability to dissect sentences at the desired level of detail?
* How do the matrices combined in figure 5f align for comparison?
* Why does the prediction view use a continuous interaction like drag when the target is to select one of only three discrete options?
* What happens in the prediction view if many predictions are close to each other? Between the predictions and the density contour map, the view could get very dense, particular if much data is involved from the 10k set.
* In the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?
* Why a treemap in the summary view? It's just a 3x3 set of quantities. A simple 3x3 matrix heatmap would be more familiar, more readable, and assure that all of the prediction/label combinations are large enough to select easily.
* The description of interaction for the E/E category in the summary view says what one can do, but it's not clear how or why.

Part of the problem is that the language is very dense in this paper. Although the grammar is acceptable, it was a slow read and there were some passages that I found all but indecipherable, such as the figure 7 caption, the last paragraph of section 5.5, and the bullet list at the end of the introduction.

There were many small errors that need correcting, too many to bother listing here. There was also some hyperbole ("stunning", "unprecedented", "vision", "paradigm") that distracts me as a serious reader and should be replaced. A thorough copyediting should fix both issues.

The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination. The scenarios essentially describe individual tasks that experts might perform in individual views. Scenario 4 goes a little further, but is brief. The paper would very much benefit from a more complete example story of how an analyst might work with the various views in concert to perform higher-level activities. For an application paper like this, some sense of those activities, and how well the tool design works for them, is needed. The last couple paragraphs of section 7 offers only a glimpse of "interrogation" as the authors say. Their conclusion (participants believe it convenient) isn't sufficiently supported. As it stands, there isn't clear justification of the many visualization design choices. A longer scenario encompassing the larger process would go a long way toward rectifying that.

The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.
Reviewer 4
Paper type
Application / Design Study
Expertise
Knowledgeable
Overall Rating
<b>4.5 - Between Accept and Strong Accept</b><br/>
Supplemental Materials
Acceptable with minor revisions (specify revisions in The Review section)
Justification
see below
The Review
This paper introduces an application that lets a user to visualize aspects of a complex neural network model, and to interactively perturb that model? its inputs, its internal state, and its expected output? and then see how those perturbations affect other elements in the system. The application looks at networks that support an natural language processing task-- investigating the relationships between ideas expressed by two different sentences-- and specifically investigating attention mechanisms that weight particular words as being more or less relevant in determining these relationships.

? The introduction is for the most part well written and clearly sets up the motivation for the NLIZE application

? I was confused by the distinction between image networks and language networks. CNNs are not only used to make binary classifications, and there are certainly challenges in image networks that do not provide ?clear meaning? and seem like they would also benefit from the proposed work. In other words, I understand the focus on NLP tasks, but the reasoning for it doesn?t seem accurate (in the 3rd paragraph of the introduction).

? It was unclear to me if the idea of perturbing a model is novel, or an extension/visualization of previously introduced work in this area applied to NLP NNs. If it?s the former (as it seems to be), then I think this needs to be emphasized in the introduction.

? The discussion of why the authors chose to focus on NLI is well articulated and interesting

? The related work is sufficiently comprehensive and clearly contextualizes the main contributions of the NLIZE application

? I appreciated the task analysis in section 4. However, it seems a bit too brief, and the tasks don?t seem to directly follow from the description of the authors experience with the NLP researchers. The scenarios described in Section 6 provide much more detail about these tasks, and Section 5 clarifies them as well, but a bit more detail here would be useful. For example, it?s not clear who the NLP researchers are, how many of them were interviewed, what type of NLP projects they were working on, etc.

? The visual interface described in Section 5 seems very useful for performing the three main tasks. Some of the elements of the application are quite dense upon first encounter, but a lot of thought has gone into how they work together to provide different windows into the NN.

? Work by Ma et al. ("Visualizing dynamic brain networks using an animated dual-representation? from EuroVis 2015) is work related to NLIZE having both graph and matrix views that complement each other and provide the same information from different perspectives, as described in Section 5.2.

? Placing the grammar dependency tree over the matrix / bipartite graph is interesting (described in Section 5 and Section 6.4). I wonder if it would make sense to use other types of annotations here, such as those created from event extraction tools or information extraction tools that would highlight other structures (besides grammar/POS) that could be useful in helping understanding the inference model. Work by Forbes et al. supports the use of semantic hypergraphs to provide richer textual annotations alongside text sequences ("Text annotation graphs: Annotating complex natural language phenomena? from LREC 2018).

? The prediction triangle/contour view is very interesting!

? In Sections 6.1 and 6.2, the application scenario gives an example of having a user perturbing the model by changing the input words (switching ?pile? with ?heap?). This updates the system and changes the inference output. Are the successful results of such an interaction remembered by the system? That is, could NLIZE be used to tweak/update the model so that, say, the ambiguity between pile and heap is automatically and more accurately resolved in future queries?

A:

? Section 6.3 is very interesting, but I don?t understand why perturbing the attention stage has less of an effect that the other perturbations. This seems like a preliminary contribution in and of itself (i.e., that using the NLIZE application leads to global understanding such as this), and worthy of further examination.

A:

In sum, this paper presents an exciting approach to analyzing complex inference models? one which could in theory be extended easily to other NLP tasks and other inference models. The visualization, although somewhat complicated, seems to aid domain experts in understanding nuances of NLI tasks, and giving them a playground in which to formulate and test hypothesis through perturbing various elements within the system and seeing how they change others. The application scenarios are all quite brief and come across as somewhat preliminary, but on the other hand, the range of tasks that are supported shows the promise of such an approach. It might make more sense to focus more on only one or two scenarios and cover them in more depth. Overall, despite some of the issues mentioned above, the paper presents innovation in interactive visualization to better understand NNs for language inference tasks, and I think this paper is a strong accept.

A:

### 2018-06-09 paper/background.tex
fix typo

These end-to-end models usually take pre-trained word vectors (numerical vector representation of individual words, in which the semantic similarities are expressed by distances in the high-dimensional vector space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, and then in the encoding stage, the pre-trained vectors are adjusted to the specialized task at hand. Subsequently, the next stage aims at finding alignment between words in the input sequences. For the NLI task, this means finding the correspondance between words from the premise sentence to the hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}). Finally, in the last stage, the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).
%
Since all these three stages of the model are trained jointly in an end-to-end fashion, it is important to explore the interaction between intermediate representations and predictions to make sense of how predictions are made inside such a model.

>>>>

These end-to-end models usually take pre-trained word vectors (numerical vector representation of individual words, in which the semantic similarities are expressed by distances in the high-dimensional vector space~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}) as input, and then in the encoding stage, the pre-trained vectors are adjusted to the specialized task at hand. Subsequently, the next stage aims at finding alignment between words in the input sequences. For the NLI task, this means finding the correspondence between words from the premise sentence to the hypothesis sentence (see details in Fig.~\ref{fig:attention} and Section~\ref{sec:attention}). Finally, in the last stage, the alignment information and the encoded vector representations are aggregated and then used as features for a classification network (last part of the end-to-end neural network).
%
Since all these three stages of the model are trained jointly in an end-to-end fashion, it is important to explore the interaction between intermediate representations and predictions to make sense of how predictions are made inside such a model.

### 2018-06-09 paper/overview.tex
fix typo

\section{NLIZE System}
In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-3}).
%
As discussed in the previous section, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affects other stages of the pipeline.
%
Such a process can be generalized as the perturbation-driven paradigm, which is used as a guiding principal for designing the proposed tool.
%
As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (i.e., adjust the prediction by making updates to the model).
%
In the following sections, we describe in detail the five major components of the proposed system, namely, the sentence view  (Section~\ref{sec:sentence}), the attention view (Section~\ref{sec:attention}), the prediction view (Section~\ref{sec:prediction}), the pipeline view (Section~\ref{sec:pipeline}), and the pair summary view (Section~\ref{sec:allPairs}).

>>>>

\section{NLIZE System}
In this section, we discuss the design and implementation of the NLIZE (pronounced as ``analyze''; see interface overview in Fig.~\ref{fig:teaser}) system, which address the visualization tasks (\textbf{T1-T3}).
%
As discussed in the previous section, the experts often analyze and obtain intuition about the model by studying how altering one part of the model affects other stages of the pipeline.
%
Such a process can be generalized as the perturbation-driven paradigm, which is used as a guiding principal for designing the proposed tool.
%
As illustrated in Fig.~\ref{fig:modelPipeline}, we enable the automated or user-guided \emph{perturbation} (i.e., replace words) of the input sentence, the \emph{perturbation} of attention (i.e., alter the alignment between sentences) inside the model, and the \emph{perturbation} of the prediction (i.e., adjust the prediction by making updates to the model).
%
In the following sections, we describe in detail the five major components of the proposed system, namely, the sentence view  (Section~\ref{sec:sentence}), the attention view (Section~\ref{sec:attention}), the prediction view (Section~\ref{sec:prediction}), the pipeline view (Section~\ref{sec:pipeline}), and the pair summary view (Section~\ref{sec:allPairs}).

### 2018-06-09 paper/relatedWorks.tex
fix typo

\textbf{Model Interpretability.}
Before one can solve the model interpretability challenge, it worth to understand what constitutes an explanation for a machine learning model.
As discussion in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning. A taxonomy is suggested~\cite{Doshi-Velez2017} to promote a more rigorous study on such a subject. In the work by Lipton~\cite{Lipton2016}, many philosophical questions related to model interpretability are examined and the study also challenged the commonly held belief that linear models are more interpretable than deep neural networks.
%
In the machine learning community, one of the most studied areas in model interpretability is the interpretation of the convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
%
These methods either identify the pattern that maximally activates a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures?), or reveals what areas in the input that contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
%
Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications. In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understand snapshot of the classifier near a specific input.
%
Despite being invaluable for generating a human understandable explanation, however, the lack of the ability to access and explore the internal states of the system limits their application. 
%which is vitally important for making sense of the inner works of a model, 
To avoid similar limitations, the proposed system enables direct access and manipulation of the internals of the model.

@@

\textbf{Visualization of NLP Models.}
Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studys have been dedicated to neural language processing models.
%
The previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models but also revealed enormous possibility for future applications.
% There is many unresolved challenges and the
The early work on character-level recurrent networks~\cite{KarpathyJohnson2015} demonstrates the effectiveness of the hidden state in capturing the unique pattern in the training text. The compositionality (i.e., build the meaning of a sentence from the meaning of words and phrases) exhibited in neural network linguistic models is examined by utilizing techniques inspired by model interpretability techniques in computer vision by Li et al. ~\cite{LiChenHovy2015}.
In the RNNVis~\cite{MingCaoZhang2017} work, Ming et al. visualize the hidden state units in a recurrent neural network based on their expected responses to model input.
The RNNbow~\cite{CashmanPattersonMosca2017} system helps domain experts understand how the model is trained by visualizing the backpropagation gradient information.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line plot style visual encoding to represent the time varying hidden states of the recurrent neural network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrates how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space (e.g., word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}).
%As discussed in the introduction, the experts guided exploration calls for the ability to interact with internal of the model in a dynamic setting. 
%
All the previously discussed NLP model visualization works either focus on the training process or examine the trained model as a fixed object. In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.
%In addition, instead of exploring a language model or low-level, the proposed method focus on a specific NLP task, which provide insight on

>>>>

\textbf{Model Interpretability.}
Before one can solve the model interpretability challenge, it worth to understand what constitutes an explanation for a machine learning model.
As discussed in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning. A taxonomy is suggested~\cite{Doshi-Velez2017} to promote a more rigorous study on such a subject. In the work by Lipton~\cite{Lipton2016}, many philosophical questions related to model interpretability are examined and the study also challenged the commonly held belief that linear models are more interpretable than deep neural networks.
%
In the machine learning community, one of the most studied areas in model interpretability is the interpretation of the convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
%
These methods either identify the pattern that maximally activates a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures?), or reveals what areas in the input that contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
%
Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which makes them applicable to different applications. In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understand snapshot of the classifier near a specific input.
%
Despite being invaluable for generating a human understandable explanation, however, the lack of the ability to access and explore the internal states of the system limits their application. 
%which is vitally important for making sense of the inner works of a model, 
To avoid similar limitations, the proposed system enables direct access and manipulation of the internals of the model.

@@

\textbf{Visualization of NLP Models.}
Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studies have been dedicated to neural language processing models.
%
The previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models but also revealed enormous possibility for future applications.
% There is many unresolved challenges and the
The early work on character-level recurrent networks~\cite{KarpathyJohnson2015} demonstrates the effectiveness of the hidden state in capturing the unique pattern in the training text. The compositionality (i.e., build the meaning of a sentence from the meaning of words and phrases) exhibited in neural network linguistic models is examined by utilizing techniques inspired by model interpretability techniques in computer vision by Li et al. ~\cite{LiChenHovy2015}.
In the RNNVis~\cite{MingCaoZhang2017} work, Ming et al. visualize the hidden state units in a recurrent neural network based on their expected responses to model input.
The RNNbow~\cite{CashmanPattersonMosca2017} system helps domain experts understand how the model is trained by visualizing the backpropagation gradient information.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line plot style visual encoding to represent the time varying hidden states of the recurrent neural network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrates how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space (e.g., word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}).
%As discussed in the introduction, the experts guided exploration calls for the ability to interact with internal of the model in a dynamic setting. 
%
All the previously discussed NLP model visualization works either focus on the training process or examine the trained model as a fixed object. In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.
%In addition, instead of exploring a language model or low-level, the proposed method focus on a specific NLP task, which provide insight on
